---
title: "Presentation Title"
author: "my name"
date: "`r Sys.Date()`"
revealjs-url: "../../../"
output: 
  Rcandoo::revealjs_format:
    theme: beige
    transition: default
---
```{r mainSettings, echo=FALSE}
library(knitr)
# knitr options
opts_chunk$set(cache = TRUE, echo = FALSE)
options(scipen=2, digits=2)
```
# R Markdown / pandoc / reveal.js

## R Markdown

This is an R Markdown presentation adapted to use the reveal.js framework for displaying the slides. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

### Using **knit**

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

#
## Sub slide header

One of the great things about reveal.js is its use of two dimensional slides. Level 1 headings create sections, level 2 headings slides within sections, and level three and below the slide content.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r, echo=TRUE}
summary(cars)
```

## Slide with Plot

```{r}
plot(cars)
```

## Slide with background image {data-background=untitled_files/figure-revealjs/unnamed-chunk-2-1.png}

## Slide with maths

$$ x^2 = y_2 $$

This should be converted to lovely MathJax.

## Slide with non-R code
```js
document.getElementById('demo').innerHTML = 'Hello Javascript!'
```
Should be syntax highlighted nicely

Note: this should work as speaker notes, but may need some work
<div class="notes">
These notes should work however, by pressing `s` while on the slides

- It can contain markdown
- like this list
</div>

## A table made from R code
```{r kableTable, results='asis'}
kable(summary(cars), align = c('r', 'l'), caption = "The caption for this table")
```

## And a table hand written

| Right | Left | Default | Center |
|------:|:-----|---------|:------:|
|   12  |  12  |    12   |    12  |
|  123  |  123 |   123   |   123  |
|    1  |    1 |     1   |     1  |

  : Demonstration of simple table syntax.